### 2021-07-29 doc/thesis/chapters/dsp.tex
hls interface
results
Fig. -> Figure

\noindent
The block diagram in Fig.\ref{fig:bd_dsp_overview} gives a high-level overview of a receiver structure.

@@

Fig.\ref{fig:bd_superhet} shows a block diagram of a superhet receiver.
The antenna signal first runs through a band selection filter.
It selects the desired frequency band and filters out any unwanted signals outside of this band.
A low-noise amplifier (LNA) may be used to boost the signal strenght.
The next step is the mixer, which is fed by a local oscillator (LO).
This shifts, or down-converts, the antenna signal down to the IF.
Afterwards, the IF signal is amplified and filtered again to remove the side-products of the mixer, namely the image replicas.
Thus, it is also called an image rejection filter.
The demodulator stage can now perform any further signal processing on the signal, until the required signal is retrieved \cite{PassosFábio2020AHSo}.\\

@@

\includepicture [1.0] {Block design of a superhetorodyne receiver \cite[Fig.2.1]{PassosFábio2020AHSo}} {bd_superhet} {img/draw.io/superheterodyne-receiver-block-diagram}

@@

\includepicture [1.0] {Block design of a direct-conversion receiver \cite[Fig.2.3]{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/draw.io/direct-conversion-receiver-block-diagram}

@@

A block diagram, as well as the signal spectrum of the process is shown in Fig.\ref{fig:bd_down_conversion_spectrum}. In this example, the frequency of the LO is set to shift the signal from $f_m$ to baseband.

@@

The procedure that is used for down-conversion is an amplitude modulation (AM).
The equation for a generic AM signal is $ S_{AM}(t) = A_m m(t) \cdot A_c c(t) $, where $m(t)$ represents the message signal, and $c(t)$ is the high-frequency carrier.
Their respective amplitudes are $A_m$ and $A_c$.
This equation is depicted as a block diagram and signal spectrum in Fig.\ref{fig:bd_down_conversion_spectrum}, where $S_{AM}$ is denoted as the baseband signal $m_{BB}$ of the original signal $m$.
The signal $m(t)$ is a baseband signal.
It may be antenna signal that was filtered by a bandpass filter.
The received signal is a real signal, and thus its negative frequency spectrum is an exact mirror of the positive frequencies.
This fact can be explained in two simple equations.\\

@@

The graphical representation in the frequency spectrum is shown in Fig.\ref{fig:down_conversion_spectrum_steps}.
As mentioned above, the assumption is a direct conversion to baseband, so $w_m = w_c$.
Looking at the positive original part, it is shown that only half of its energy is translated into the desired baseband.
However, half of the energy of the original negative part is also shifted to baseband.
The superposition of the two parts results in an amount of energy that is again equal to the original signal.

@@

In words: The sampling frequency must be higher than twice the frequency of the signals' highest frequency content.
Any digital signal processing technique must hold the specification of the sampling theorem \cite[chpt. 4.2]{AlessioSilviaMaria2016DSPa}.
In case the theorem is violated, the effect of aliasing occurs on the generated signal.
The sampling process introduces spectral replicas at integer multiples of the sampling frequency $f_s$.
These replicas overlap, if $f_s$ does not meet the theorem, which results in signal distortion.
Fig.\ref{fig:aliasing_freq_spectrum} illustrates the effect of aliasing in the frequency spectrum \cite{ThyagarajanK.S2019ItDS}.

@@

Fig.\ref{fig:fm_channel_baseband_freqs} shows the frequency spectrum of a single channel, located at its carrier- or center frequency.
For a better overview, only the positive spectum part is shown.
The negative part is an exact mirror, because the transmitted and received signals from the antenna are real signals - they do not have an imaginary part.
The spectrum consists of multiple parts. Therefore, it is also referred to as `multiplex signal' in the literature. Several parts are described in the following paragraphs \cite{EbuFmRegulators}\cite{EtsiFmSoundBroadcastingServiceHarmonizedStandard}\cite{ElectronicsNotesFmTutorial}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Baseband Delay Demodulator}
\label{sec:BasebandDelayDemodulator}
TODO\\
see /home/mike/Dropbox/Studium/ma\_semester\_4\_SS21/ma/literature/FmDemodulator.pdf

@@

A frequency discriminator generates an output that is directly proportional to the frequency of the input FM signal.
In other words, it converts FM to AM.
The discriminator consists of two main parts - a differentiator and an envelope detector.
Different strategies can be implemented for both parts.
A block diagram for a frequency discriminator with its two main parts is shown in Fig.\ref{fig:bd_freq_discriminator}.

@@

A time-domain example for this signal is shown in the top left diagram in Fig.\ref{fig:time_domain_envelope_detect}.\\

@@

The differentiated signal still consists of a FM part, as explained above, using Eq.\eqref{equ:fm_demod_discriminator}.
In order to remove this high-frequeny part and extract the low-frequency envelope, the signal needs to be fed into an envelope detector.
A block diagram is shown in Fig.\ref{fig:bd_freq_discriminator}.\\

The method implemented in Fig.\ref{fig:time_domain_envelope_detect} is one of the most simple ones and is usually referred to as `Asynchronous Half-Wave Envelope Detector' \cite{DSPRelatedEnvelopeDetection}.
It consists of a thresholding unit to remove negative values and a conventional lowpass filter.
In analog implementations, the thresholding unit is a diode.
The cutoff frequency of the lowpass needs to be adapted to the envelope signals' maximum frequency.
It needs to be able to follow the signal, but also sufficiently smooth out the rectified signal.\\

@@

A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.

@@

The block diagram in Fig.\ref{fig_bd_stereo_demod} illustrates the signal processing chain for stereo audio.
In the block diagram, $x(t)$ represents the multiplex signal from the FM demodulator.
The signals $x_l(t)$ and $x_r(t)$ describe the left and right audio signal, respectively.\\

>>>>

\noindent
The block diagram in Figure \ref{fig:bd_dsp_overview} gives a high-level overview of a receiver structure.

@@

Figure \ref{fig:bd_superhet} shows a block diagram of a superhet receiver.
The antenna signal first runs through a band selection filter.
It selects the desired frequency band and filters out any unwanted signals outside of this band.
A low-noise amplifier (LNA) may be used to boost the signal strenght.
The next step is the mixer, which is fed by a local oscillator (LO).
This shifts, or down-converts, the antenna signal down to the IF.
Afterwards, the IF signal is amplified and filtered again to remove the side-products of the mixer, namely the image replicas.
Thus, it is also called an image rejection filter.
The demodulator stage can now perform any further signal processing on the signal, until the required signal is retrieved \cite{PassosFábio2020AHSo}.\\

@@

\includepicture [1.0] {Block design of a superhetorodyne receiver \cite{PassosFábio2020AHSo}} {bd_superhet} {img/draw.io/superheterodyne-receiver-block-diagram}

@@

\includepicture [1.0] {Block design of a direct-conversion receiver \cite{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/draw.io/direct-conversion-receiver-block-diagram}

@@

A block diagram, as well as the signal spectrum of the process is shown in Figure \ref{fig:bd_down_conversion_spectrum}. In this example, the frequency of the LO is set to shift the signal from $f_m$ to baseband.

@@

The procedure that is used for down-conversion is an amplitude modulation (AM).
The equation for a generic AM signal is $ S_{AM}(t) = A_m m(t) \cdot A_c c(t) $, where $m(t)$ represents the message signal, and $c(t)$ is the high-frequency carrier.
Their respective amplitudes are $A_m$ and $A_c$.
This equation is depicted as a block diagram and signal spectrum in Figure \ref{fig:bd_down_conversion_spectrum}, where $S_{AM}$ is denoted as the baseband signal $m_{BB}$ of the original signal $m$.
The signal $m(t)$ is a baseband signal.
It may be antenna signal that was filtered by a bandpass filter.
The received signal is a real signal, and thus its negative frequency spectrum is an exact mirror of the positive frequencies.
This fact can be explained in two simple equations.\\

@@

The graphical representation in the frequency spectrum is shown in Figure \ref{fig:down_conversion_spectrum_steps}.
As mentioned above, the assumption is a direct conversion to baseband, so $w_m = w_c$.
Looking at the positive original part, it is shown that only half of its energy is translated into the desired baseband.
However, half of the energy of the original negative part is also shifted to baseband.
The superposition of the two parts results in an amount of energy that is again equal to the original signal.

@@

In words: The sampling frequency must be higher than twice the frequency of the signals' highest frequency content.
Any digital signal processing technique must hold the specification of the sampling theorem \cite[chpt. 4.2]{AlessioSilviaMaria2016DSPa}.
In case the theorem is violated, the effect of aliasing occurs on the generated signal.
The sampling process introduces spectral replicas at integer multiples of the sampling frequency $f_s$.
These replicas overlap, if $f_s$ does not meet the theorem, which results in signal distortion.
Figure \ref{fig:aliasing_freq_spectrum} illustrates the effect of aliasing in the frequency spectrum \cite{ThyagarajanK.S2019ItDS}.

@@

Figure \ref{fig:fm_channel_baseband_freqs} shows the frequency spectrum of a single channel, located at its carrier- or center frequency.
For a better overview, only the positive spectum part is shown.
The negative part is an exact mirror, because the transmitted and received signals from the antenna are real signals - they do not have an imaginary part.
The spectrum consists of multiple parts. Therefore, it is also referred to as `multiplex signal' in the literature. Several parts are described in the following paragraphs \cite{EbuFmRegulators}\cite{EtsiFmSoundBroadcastingServiceHarmonizedStandard}\cite{ElectronicsNotesFmTutorial}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Baseband Delay Demodulator}
%\label{sec:BasebandDelayDemodulator}
%TODO\\
%see /home/mike/Dropbox/Studium/ma\_semester\_4\_SS21/ma/literature/%FmDemodulator.pdf

@@

A frequency discriminator generates an output that is directly proportional to the frequency of the input FM signal.
In other words, it converts FM to AM.
The discriminator consists of two main parts - a differentiator and an envelope detector.
Different strategies can be implemented for both parts.
A block diagram for a frequency discriminator with its two main parts is shown in Figure \ref{fig:bd_freq_discriminator}.

@@

A time-domain example for this signal is shown in the top left diagram in Figure \ref{fig:time_domain_envelope_detect}.\\

@@

The differentiated signal still consists of a FM part, as explained above, using Eq.\eqref{equ:fm_demod_discriminator}.
In order to remove this high-frequeny part and extract the low-frequency envelope, the signal needs to be fed into an envelope detector.
A block diagram is shown in Figure \ref{fig:bd_freq_discriminator}.\\

The method implemented in Figure \ref{fig:time_domain_envelope_detect} is one of the most simple ones and is usually referred to as `Asynchronous Half-Wave Envelope Detector' \cite{DSPRelatedEnvelopeDetection}.
It consists of a thresholding unit to remove negative values and a conventional lowpass filter.
In analog implementations, the thresholding unit is a diode.
The cutoff frequency of the lowpass needs to be adapted to the envelope signals' maximum frequency.
It needs to be able to follow the signal, but also sufficiently smooth out the rectified signal.\\

@@

A frequency spectrum of the multiplex signal of an FM channel is shown in Figure \ref{fig:fm_channel_baseband_freqs}.

@@

The block diagram in Figure \ref{fig_bd_stereo_demod} illustrates the signal processing chain for stereo audio.
In the block diagram, $x(t)$ represents the multiplex signal from the FM demodulator.
The signals $x_l(t)$ and $x_r(t)$ describe the left and right audio signal, respectively.\\

### 2021-07-29 doc/thesis/chapters/hls.tex
Fig. -> Figure

A major achievement in the usage of HLS is the shorter development time.
The time that it takes to develop a first working version of the intended design can be significantly reduced, compared to the development in RTL code directly.
This is especially important when an FPGA design is combined with a software part, like in a System On Chip, since software development is comparably fast.
Fig.\ref{fig:timeline_performance_first_prototype} schematically displays the difference in development time, over performance and degree of optimization, when the same functionality of a prototype is implemented in different methods for various targets.
The compared targets are an x86 processor CPU, a digital signal processor (DSP), a graphics processing unit (GPU) and the FPGA design in RTL or HLS implementation.
It is clearly visible, that the FPGA design with the HLS design approach achieves a first working prototype much earlier than the direct RTL approach.

>>>>

A major achievement in the usage of HLS is the shorter development time.
The time that it takes to develop a first working version of the intended design can be significantly reduced, compared to the development in RTL code directly.
This is especially important when an FPGA design is combined with a software part, like in a System On Chip, since software development is comparably fast.
Figure \ref{fig:timeline_performance_first_prototype} schematically displays the difference in development time, over performance and degree of optimization, when the same functionality of a prototype is implemented in different methods for various targets.
The compared targets are an x86 processor CPU, a digital signal processor (DSP), a graphics processing unit (GPU) and the FPGA design in RTL or HLS implementation.
It is clearly visible, that the FPGA design with the HLS design approach achieves a first working prototype much earlier than the direct RTL approach.

### 2021-07-29 doc/thesis/chapters/implementation.tex
results wip..
Fig. -> Figure

\noindent
Fig.\ref{fig:bd_dsp_detailed} displays the detailed DSP chain as a block diagram.\\

@@

  \item \textbf{FM Demodulator}\\
      The FM demodulator is implemented as a Baseband Delay Modulator, as described in Section \ref{sec:BasebandDelayDemodulator}.

@@

The transmitter is implemented according to the structure that is depicted as a block diagram in Fig.\ref{fig:bd_matlab_transmitter}.
To facilitate an easy understanding of the block diagram, it is of advantage to keep in mind that it exactly resembles the frequency spectrum that is previously shown in Fig.\ref{fig:fm_channel_baseband_freqs}.\\

@@

At this point in the DSP chain, the signal resembles the frequency spectrum that is displayed in Fig.\ref{fig:fm_channel_baseband_freqs}.\\

@@

The receiver is implemented, following the block diagram in Fig.\ref{fig:bd_dsp_detailed}.
Further assumptions and simplifications, such as the fixed point arithmetic are described into detail above.

@@

An example of a plot that is created by the analysis is depicted in Fig.\ref{fig:matlab_analysis_time_domain}.
The diagram shows the respective signals in the time domain.
Above two timelines display the input data, as it is read from the input audio file.
The two diagrams in the center plot the Mono and LR Diff signals.
The bottom diagrams then represent the result after the entire signal processing chain.
It can be seen that the DSP chain is not able to demodulate the original signal without any error.
However, the result shows a clear separation of the left and right channels, as resembles the original input very closely, which is good enough for this case study.\\

@@

Further analysis is done in the frequency domain, especially in order to better understand the modulation of the different spectral parts in the FM channel.
An example thereof is shown in Fig.\ref{fig:matlab_analysis_freq_domain}.
The spectrum of an FM channel multiplex signal, as it is generated by a transmitter before the modulation, is shown in this diagram.
The spectrum after the demodulation through a receiver is shown in the lower diagram.
Spectral parts, such as the pilot tone at 19 kHz, or the LR Diff part around 38 kHz can be seen clearly.
The demodulated spectrum shows an artifact at 57 kHz, which does not exist in the original transmitter spectrum.
This is an artifact of the demodulation process, specifically the frequency-shift of the LR Diff part to baseband.
The artifact is very low in energy, because it is attenuated by a BP filter in the down-conversion process, and can thus be ignored for further processing, even though it can still be seen in the spectral analysis.

@@

GNU Radio provides a comprehensive set of DSP blocks, which are available to build various functionalities.
Multiple blocks are connected to a block diagram, that is very similar to the one in Fig.\ref{fig:bd_matlab_transmitter}.
The USRP device is used to broadcast the RF signal over the air.\\

@@

\noindent
Fig.\ref{fig:bd_gnuradio_setup_transmitter} shows a block diagram of the transmitter application.

@@

This receiver works with both devices, the USRP b200mini and the RTL-SDR.
Fig.\ref{fig:bd_gnuradio_setup_receiver} shows a block diagram of the receiver application.

@@

Fig.\ref{fig:bd_cocotb_interface_simulator} gives an overview of how cocotb interfaces with a simulator.
The Python test cases are shown as a list of coroutines, which are managed by a scheduler.
This Python code interfaces with the simulator through standard interfaces like VPI.
The block called \textit{GPI} is developed by cocotb and abstracts the different simulator interfaces, such as VPI, VHPI or FLI.
In the simulator, the device under test (DUT) is instantiated.
The RTL simulation itself is managed by the simulators' scheduler.

@@

Fig.\ref{fig:bd_testbench_architecture_vhdl} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual simulator interfaces, as described in \ref{sub:VHDL:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

@@

Fig.\ref{fig:register_engine} gives an overview of how the Register Engine script works.
The Python script takes the register definitions from the YAML file, and uses templates to generate the respecitive output files.\\

@@

Fig.\ref{fig:testbench_hls_overview_reuse} gives an overview of the testbench and specifically points out the reuse of the application software.
The diagram displays the HLS IP in the testbench and in the hardware with dotted lines, to emphasize that they are actually the same.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

>>>>

\noindent
Figure \ref{fig:bd_dsp_detailed} displays the detailed DSP chain as a block diagram.\\

@@

  \item \textbf{FM Demodulator}\\
       TODO\\
       % TODO
      The FM demodulator is implemented as a Baseband Delay Modulator, as described in Section \ref{sec:BasebandDelayDemodulator}.

@@

The transmitter is implemented according to the structure that is depicted as a block diagram in Figure \ref{fig:bd_matlab_transmitter}.
To facilitate an easy understanding of the block diagram, it is of advantage to keep in mind that it exactly resembles the frequency spectrum that is previously shown in Figure \ref{fig:fm_channel_baseband_freqs}.\\

@@

At this point in the DSP chain, the signal resembles the frequency spectrum that is displayed in Figure \ref{fig:fm_channel_baseband_freqs}.\\

@@

The receiver is implemented, following the block diagram in Figure \ref{fig:bd_dsp_detailed}.
Further assumptions and simplifications, such as the fixed point arithmetic are described into detail above.

@@

An example of a plot that is created by the analysis is depicted in Figure \ref{fig:matlab_analysis_time_domain}.
The diagram shows the respective signals in the time domain.
Above two timelines display the input data, as it is read from the input audio file.
The two diagrams in the center plot the Mono and LR Diff signals.
The bottom diagrams then represent the result after the entire signal processing chain.
It can be seen that the DSP chain is not able to demodulate the original signal without any error.
However, the result shows a clear separation of the left and right channels, as resembles the original input very closely, which is good enough for this case study.\\

@@

Further analysis is done in the frequency domain, especially in order to better understand the modulation of the different spectral parts in the FM channel.
An example thereof is shown in Figure \ref{fig:matlab_analysis_freq_domain}.
The spectrum of an FM channel multiplex signal, as it is generated by a transmitter before the modulation, is shown in this diagram.
The spectrum after the demodulation through a receiver is shown in the lower diagram.
Spectral parts, such as the pilot tone at 19 kHz, or the LR Diff part around 38 kHz can be seen clearly.
The demodulated spectrum shows an artifact at 57 kHz, which does not exist in the original transmitter spectrum.
This is an artifact of the demodulation process, specifically the frequency-shift of the LR Diff part to baseband.
The artifact is very low in energy, because it is attenuated by a BP filter in the down-conversion process, and can thus be ignored for further processing, even though it can still be seen in the spectral analysis.

@@

GNU Radio provides a comprehensive set of DSP blocks, which are available to build various functionalities.
Multiple blocks are connected to a block diagram, that is very similar to the one in Figure \ref{fig:bd_matlab_transmitter}.
The USRP device is used to broadcast the RF signal over the air.\\

@@

\noindent
Figure \ref{fig:bd_gnuradio_setup_transmitter} shows a block diagram of the transmitter application.

@@

This receiver works with both devices, the USRP b200mini and the RTL-SDR.
Figure \ref{fig:bd_gnuradio_setup_receiver} shows a block diagram of the receiver application.

@@

Figure \ref{fig:bd_cocotb_interface_simulator} gives an overview of how cocotb interfaces with a simulator.
The Python test cases are shown as a list of coroutines, which are managed by a scheduler.
This Python code interfaces with the simulator through standard interfaces like VPI.
The block called \textit{GPI} is developed by cocotb and abstracts the different simulator interfaces, such as VPI, VHPI or FLI.
In the simulator, the device under test (DUT) is instantiated.
The RTL simulation itself is managed by the simulators' scheduler.

@@

Figure \ref{fig:bd_testbench_architecture_vhdl} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual simulator interfaces, as described in \ref{sub:VHDL:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}
\label{sec:impl:vhdl:interfaces}

@@

Figure \ref{fig:register_engine} gives an overview of how the Register Engine script works.
The Python script takes the register definitions from the YAML file, and uses templates to generate the respecitive output files.\\

@@

Figure \ref{fig:testbench_hls_overview_reuse} gives an overview of the testbench and specifically points out the reuse of the application software.
The diagram displays the HLS IP in the testbench and in the hardware with dotted lines, to emphasize that they are actually the same.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}
\label{sec:impl:hls:interfaces}

### 2021-07-29 doc/thesis/chapters/system-architecture-and-concept.tex
spelling
Fig. -> Figure

%%%%%%%%%%%%%%%%%%%%
\section{The project}

@@

\noindent
A very high-level overview of the entire system is given by the block diagram in Fig.\ref{fig:bd_system_overview_highlevel}.
It shows the front end, which processes the received antenna signal, so that it can be used in the FM radio receiver block.
The radio receiver itself is implemented in multiple different variants.
The produced audio output is sent to a speaker, since the ultimate goal is to listen to a radio stations' audio signal.

@@

%%%%%%%%%%%%%%%%%%%%
\section{System concept}

@@

An example of a system concept and its architecture is developed and shown in Fig.\ref{fig:bd_system_overview_detailed}.
Here, a common data source is provided by the block called \textit{Front End}.
It records data from an antenna and saves it to a file, in a format that the consequent blocks require at their input.
Therefore, a reproducable input is ensured.
Within the \textit{FM Radio Receiver} block, all the different implementation variants are shown in parallel.
They all work on this common input source and generate their respective output.
This output data is again written to a file.
Hereby it is important to note, that the output of the \textit{Matlab} implementation is chosen to be the 'golden reference model' of correct output.
Its output is used as the verification data later in the process.
This is because Matlab was used to research decoding algorithms and to develop the DSP chain, which is used in the GNU Radio, HLS and VHDL implementations.
In addition to the verification data, the Matlab model also writes common parameters to a file.
These parameters are directly used in the other implementations, to ensure a common setup.
The final block is the \textit{Verification} entity, which compares the output files of all the variants, with respect to the chosen model parameters.\\

>>>>

%%%%%%%%%%%%%%%%%%%%
\section{The Project}

@@

\noindent
A very high-level overview of the entire system is given by the block diagram in Figure \ref{fig:bd_system_overview_highlevel}.
It shows the front end, which processes the received antenna signal, so that it can be used in the FM radio receiver block.
The radio receiver itself is implemented in multiple different variants.
The produced audio output is sent to a speaker, since the ultimate goal is to listen to a radio stations' audio signal.

@@

%%%%%%%%%%%%%%%%%%%%
\section{System Concept}

@@

An example of a system concept and its architecture is developed and shown in Figure \ref{fig:bd_system_overview_detailed}.
Here, a common data source is provided by the block called \textit{Front End}.
It records data from an antenna and saves it to a file, in a format that the consequent blocks require at their input.
Therefore, a reproducable input is ensured.
Within the \textit{FM Radio Receiver} block, all the different implementation variants are shown in parallel.
They all work on this common input source and generate their respective output.
This output data is again written to a file.
Hereby it is important to note, that the output of the \textit{Matlab} implementation is chosen to be the 'golden reference model' of correct output.
Its output is used as the verification data later in the process.
This is because Matlab was used to research decoding algorithms and to develop the DSP chain, which is used in the GNU Radio, HLS and VHDL implementations.
In addition to the verification data, the Matlab model also writes common parameters to a file.
These parameters are directly used in the other implementations, to ensure a common setup.
The final block is the \textit{Verification} entity, which compares the output files of all the variants, with respect to the chosen model parameters.\\

### 2021-07-29 doc/thesis/chapters/system-design-process.tex
Fig. -> Figure

Each of these terms represents a separate step in the process diagram shown in Fig.\ref{fig:similar_process}.
The steps can be seen as iterative and parallel, as the process runs during the product development cycle.

@@

A well-known process model is the so called V-Model.
It is based on the similarly well-known Waterfall Model, and has its name because of the distinct V-shape of its process diagram, as it is shown in Fig.\ref{fig:v_modell}.
One of the main characteristics of the V-Model is, that one phase needs to be completed before the following phase can start.
This classifies the model as a static process model and is one of the main disadvantages at the same time, because it makes the model inflexible to adaptions of the requirements.
The advantages however are that it is easy to install and apply, each phase has its specific deliverables, good results can be achieved for large projects with simple requirements and the early test phases.\\

@@

Furthermore, the V-model diagram in Fig.\ref{fig:v_modell} shows the difference between validation and verification, as it is explained in the previous section \ref{sec:ValidationAndVerification}.

@@

Fig. \ref{fig:simulink_system_generator} shows this entire design approach in a block diagram.
The abbreviation ISE stands for Integrated Software Environment, and is Xilinx' development environment that includes the FPGA synthesis tool.
ModelSim is a HDL simulator software, that is developed by Mentor Graphics.

@@

Multiple implementation methods are introduced in above sections, which all have different levels of abstraction.
VHDL and Verilog require, or allow, a very detailed description of the RTL code, while SystemC, \cplusplus, or Matlab and Simulink provide a high level of abstraction.
In Fig.\ref{fig:fpga_design_levels}, the various implementation methods are compared.
The respective level of abstraction is higher towards the upper end, while the level of detail increases towards the bottom of the figure.\\

>>>>

Each of these terms represents a separate step in the process diagram shown in Figure \ref{fig:similar_process}.
The steps can be seen as iterative and parallel, as the process runs during the product development cycle.

@@

A well-known process model is the so called V-Model.
It is based on the similarly well-known Waterfall Model, and has its name because of the distinct V-shape of its process diagram, as it is shown in Figure \ref{fig:v_modell}.
One of the main characteristics of the V-Model is, that one phase needs to be completed before the following phase can start.
This classifies the model as a static process model and is one of the main disadvantages at the same time, because it makes the model inflexible to adaptions of the requirements.
The advantages however are that it is easy to install and apply, each phase has its specific deliverables, good results can be achieved for large projects with simple requirements and the early test phases.\\

@@

Furthermore, the V-model diagram in Figure \ref{fig:v_modell} shows the difference between validation and verification, as it is explained in the previous section \ref{sec:ValidationAndVerification}.

@@

Figure \ref{fig:simulink_system_generator} shows this entire design approach in a block diagram.
The abbreviation ISE stands for Integrated Software Environment, and is Xilinx' development environment that includes the FPGA synthesis tool.
ModelSim is a HDL simulator software, that is developed by Mentor Graphics.

@@

Multiple implementation methods are introduced in above sections, which all have different levels of abstraction.
VHDL and Verilog require, or allow, a very detailed description of the RTL code, while SystemC, \cplusplus, or Matlab and Simulink provide a high level of abstraction.
In Figure \ref{fig:fpga_design_levels}, the various implementation methods are compared.
The respective level of abstraction is higher towards the upper end, while the level of detail increases towards the bottom of the figure.\\
